### 2014-11-13 tex/precise.tex
committing changes

\section{Generating Summary Heaps}
\label{sec:precise}
There are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to complete field
access and field write, and (iii) rules to check equality and
inequality of references. The other rules are common to both $\rsym$
and $\rgse$.

@@

Initialization of uninitialized references in the $\rgse$ relation is
a non-deterministic choice that creates a heap either for
the initialization of the reference to null, a new instance of
the object, or to any type compatible object in the input heap (e.g.,
previously initialized by $\rgse$). In contrast, initialization in the
$\rsym$ relation creates a single summary heap containing all of the
possible initialization choices.

@@

The initialization rules, \figref{fig:symInit}, are invoked whenever
a field containing an uninitialized reference is accessed. The
interaction with the solver in the definition of the rules is denoted
by $\mathbb{S}(\phi)$ where it returns true if $\phi$ is
satisfiable. The end rule is active when there is nothing to
initialize. This condition is determined by the function
$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location pairs
where the field $\cfgnt{f}$ is uninitialized.
\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]
A pair in the set means the field in the location maps to a reference
that then points to $\cfgnt{l}_\mathit{un}$, and that the path to that
location is feasible on some aliasing assignment.

>>>>

\section{Generating Summary Heaps}
\label{sec:precise}
In this section we present the summary heap algorithm that operates on
the bipartiate graph described in the previous section.  The summary
heap algorithm initializes, updates, and partitions the heap. It only
partitions the heap at points of divergence in the control flow graph
such as field accesses or writes (exeception control flow due to null
pointers) or comparisons of references (program control flow). There
are three sets of rewrite rules specific to the summary heap
algorithm: (i) rules to initialize symbolic references, (ii) rules to
complete field access and field write, and (iii) rules to check
equality and inequality of references. The other rules are common to
both $\rsym$ and $\rgse$. The complete set of rules are shown in the
supplemental attached with the paper.

@@

Initialization of references in GSE ($\rgse$ relation) is a
non-deterministic choice where the reference in the heap is
initialized to null, a new instance of the object, or to any type
compatible object in the input heap (e.g., previously initialized by
$\rgse$). In contrast, initialization in the $\rsym$ relation creates
a single summary heap containing all of the possible initialization
choices.

@@

The initialization rules, \figref{fig:symInit}, are invoked whenever a
field pointing to an uninitialized reference is accessed. The
interaction with the solver in the definition of the rules is denoted
by $\mathbb{S}(\phi)$ which returns true if $\phi$ is satisfiable. The
summarize-end rule becomes active when there is nothing to
initialize. This condition is determined by the function
$\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) =
\{\lp\phi\ \cfgnt{l}\rp\ ...\}$ which returns constraint-location
pairs where the field $\cfgnt{f}$ is uninitialized.
\[
\begin{array}{rcl}
\mathbb{UN}(\cfgnt{L}, \cfgnt{R}, \cfgnt{r}, \cfgnt{f}) & = &\{ \lp\phi\ \cfgnt{l}\rp \mid \lp \phi\ \cfgnt{l}\rp  \in \cfgnt{L}\lp \cfgnt{r}\rp  \wedge \\
& & \ \ \ \ \exists \phi^\prime \lp \lp \phi^\prime\ \cfgnt{l}_\mathit{un}\rp  \in \cfgnt{L}\lp \cfgnt{R}\lp l,\cfgnt{f}\rp\rp \wedge \\
& & \ \ \ \ \ \ \ \ \mathbb{S}\lp \phi \wedge \phi^\prime \rp\rp\}\\
\end{array}
\]
A pair in the set means the field in the location maps to a reference
that then points to $\cfgnt{l}_\mathit{un}$, and that the path to that
location is feasible on some aliasing assignment.
